\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\title{\textbf{The Balanchine Chain: A Validator's Ledger of Lineage}}
\author{Allison Van Cura}
\date{}

\maketitle

\begin{abstract}
In ballet as in blockchain, truth is rendered through repetition.\
Each dancer becomes both executor and validator --- a node in the\
distributed network of embodied intelligence. Balanchine's\
\textit{plotless} ballets encode motion as message: the economy\
of movement mirrors the economy of trust.
\end{abstract}

\section{Input: Concealed Variables}
Let the dancer $D_i$ represent a node in the choreographic ledger.\
The concealed variable $\kappa$ holds identity, data, and truth,\
masked within each movement $m$ from the sequence $\{m_1, m_2, \ldots, m_n\}$.\
Balanchine's teachings function as cryptographic keys, granting\
select access to the choreography's source code. The ledger stores\
not just steps but the metadata of lineage, the whispered timing,\
the placement of the gaze. The initial condition is always the\
genesis block: the first staging that anchors all future forks.

\section{Process: Recursive Reflection}
The Trust operates as a proof-of-work consensus: the \textit{work}\
is rehearsal; the \textit{proof} is performance. Each iteration\
cycles through observation, concealment, and risk. Dancers audit\
records with their bodies, refining the concealed variable $\kappa$\
without exposing it. The recursive process is encoded by
\[
\text{Integrity}(D_i, m) = \text{Faith}(m) \times \text{Precision}(D_i),
\]
with thresholds $\tau$ negotiated collectively in the studio.\
Martha Graham's \emph{queer divine dissatisfaction} acts as the\
network's liveness property, ensuring no validator rests on a\
closed block. Instead, each pass adds entropy, a necessary risk\
that prevents stagnation and preserves resilience against forks.

\section{Output: Revelation}
When $\text{Integrity} \geq \tau$, the motion is validated and appended\
to the chain. Revelation emerges as order, alignment, and eventual\
return to the score. Botticelli's Venus surfaces here as a protocol\
for liquidity: the body rises from silence with encoded grace,\
translating hidden variables into observable alignment. The stage\
becomes a transparent ledger where once-concealed truths appear\
without surrendering the sanctity of the key.

\section{Reward Function: Integrity/Resonance}
The reward is a coupled vector --- integrity sustained, resonance\
amplified. Validators receive no coin but accrue lineage credits,\
quantified as an Integrity/Resonance score broadcast through\
performance. Audiences respond with synchronized breath; fellow\
artists feel the ledgers align. The system's token is trust itself:\
a self-custodied asset held in muscle memory, paid forward each\
time the choreography re-enters circulation.

\end{document}
